Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-09-30 paper/review/response-to-review.Rmd

Additional comments:

Please add some discussion on what kind of functionality is available in 
other statistical software packages than R in order to better embed the 
contribution not only within R, but the statistical software ecosystem in 
general.

> We have added the following at the end of section 3:

> Missing data can be explored and visualised in other software such as \proglang{STATA}, \proglang{SAS}, and \proglang{SPSS}. They provide basic table frequencies of missing data, and basic visualisations on missingness patterns. However, none of these software provide functions to specifically visualise missing values in bivariate or multivariate settings, and it is only possible to visualise missing values after performing data analysis, counting and summarising missingness. Imputation methods from mean to regression, EM, and multiple imputation are all available, with out of the box diagnostics provided to assist comparing imputations. \proglang{python} also provides exploratory data analysis for missing data within \pkg{missingno} [@Bilogur2018], and the \pkg{scikit-learn} package provides imputation methods [@scikit-learn].

@@

Please provide a plain R script which when run reproduces all results 
presented in the manuscript. In general purling the Rmd file and editing 
the resulting R file  slightly in order to guide the user what each block 
does, removing knitr specific content,   etc. is suitable.

> We have added a file, "tidy-missingdata-paper.R" that contains the R code from the paper

* The JSS style (https://www.jstatsoft.org/pages/view/style) should be 
followed more closely, especially using the title vs. sentence case, 
JSS-specific markup (\proglang, \pkg), and improving the BibTeX file. Some 
aspects of the style are handled incorrectly by "rticles", though (see
https://github.com/rstudio/rticles/issues/254).

> I have updated to the latest rticles package and checked that the JSS-specific markup has been fixed in the latest submission. Many instances of \proglang, \pkg, and \code have been used now

### 2020-09-30 paper/tidy-missing-data-paper.Rmd
tidying up some of the tables

<!-- (NOTE: Is the last sentence OK?) -->

<!-- (NOTE: trying to come up with a sentence that leads from this section to the next) -->

@@

<!-- Note: Do you think this paragraph needs to be here, about the use of _nabular_ data structure? -->

@@

Special missing values are not a new idea, and have been implemented in other statistical programming languages, \proglang{SPSS}, \proglang{SAS}, and \proglang{STATA}. These typically represent missing values as a full-stop, `.`, and record special missing values as `.a` - `.z`. These special values from these languages break the tidy principle of one column having one type of value, as they record both the value, and the multivariate missingness state.

@@

```{r impute-summary-out, echo = FALSE}
aq_imputed %>%
  group_by(any_missing) %>%
  summarise_at(.vars = vars(Ozone),
               .funs = lst(min, mean, median, max))  %>% 
  kable(caption = "Summarising values of imputed vs non imputed values. Comparing imputed values (denoted as 'Missing', since they were previously missing), the mean and median values are similar, but the minimum and maximum values are very different.")
```

@@

miss_var_table(airquality) %>% 
  knitr::kable(
    caption = "\\texttt{miss\\char`_var\\char`_table} tabulates the amount of missing data in each variable in airquality. This shows the number of variables with 0, 7, and 37 missings, and the percentage of variables with those amounts of missingness. There are few missingness patterns.",
    digits = 1)
    # booktabs = TRUE)
  # kable_styling(latex_options = c("hold_position"))
```

>>>>

@@

@@

Special missing values are not a new idea, and have been implemented in other statistical programming languages, \proglang{SPSS}, \proglang{SAS}, and \proglang{STATA}. These typically represent missing values as a full-stop, ".", and record special missing values as ".a" - ".z". These special values from these languages break the tidy principle of one column having one type of value, as they record both the value, and the multivariate missingness state.

@@

```{r impute-summary-out, echo = FALSE}
aq_imputed %>%
  group_by(any_missing) %>%
  summarise_at(.vars = vars(Ozone),
               .funs = lst(min, mean, median, max))  %>% 
  kable(caption = "Output of \\pkg{dplyr} summary statistics of imputed vs non imputed values for the variable 'Ozone'. The 'any\\_missing' column denotes imputed values ('Missing', since they were previously missing), and non-imputed values ('Not Missing'). The mean and median values are similar, but the minimum and maximum values are very different.")
```

@@

miss_var_table(airquality) %>% 
  knitr::kable(
    caption = "The output of \\code{miss\\char`_var\\char`_table(airquality)}, tabulating the amount of missing data in each variable in airquality. This shows the number of variables with 0, 7, and 37 missings, and the percentage of variables with those amounts of missingness. There are few missingness patterns.",
    digits = 1)
    # booktabs = TRUE)
  # kable_styling(latex_options = c("hold_position"))
```
